### 2017-03-29 paper/evaluation.tex
pass on text

\Jbc{these results will be updated $\rightarrow$}
It is important to mention that Figure~\ref{fig:rq1-barplot}
represents a lower bound estimation for time cost because some
projects omit long-running tests on their default execution. For
instance, it is necessary to invoke Maven with additional parameters
to run integration tests from project \CodeIn{apache.maven-surefire}
(nearly 30 min in our environment).  Also, some tests may finish
earlier than expected due to existing bugs on the ongoing revision.
From the \numSubjs{} compiled projects, 286 successfully executed
all tests and 118 reported test failures.

@@

To evaluate the support of parallelization in test suites, we
considered all projects classified as \medg{} and \longg{}-running, a
total of \numMedLong{} subjects (see Figure~\ref{fig:rq1-barplot}). To
reduce noise we did not consider projects with \shortg{}-running test
suites as we observed that \percentShortSequential{} of those projects
do not use parallelism; including them would favor sequential
execution in our analysis.

To answer \numRQC{} we initially configured Maven to output
configuration settings and re-executed the tests to collect and
classify the test suites according to its level of parallelization
(see Section \ref{sec:modes}).  The rationale is that if a test suite
is configured to run in parallel, Maven is going to display the
configuration and we can classify it according to its parallelization
level.  We are interested to know how frequent are parallel executions
and what configurations are more popular.  According to Maven's
documentation\Fix{cite surefire doc}, the set of parameters to run
tests in parallel is described as follows: \CodeIn{parallel} defines
the parallelism granularity within a JVM (\eg, methods or classes);
\CodeIn{threadCounter} defines the size of the thread pool; and
\CodeIn{forkCount} defines the number of forked JVMs. Additional
options exists and depends on theses parameters to take effect. To
avoid waiting all tests to terminate, we just run the bootstrap phase
and we skip the actual test execution. \Jbc{Missing: explain how we
mapped the configurations to parallel level.}
Figure~\ref{fig:freqmodes-dynamic} summarizes our findings.

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.32\textwidth]{plots/barplot-modes-dynamic.pdf}
    \caption{\label{fig:freqmodes-dynamic}Distribution of parallel modes 
    identified dynamically in a subset of \numProjectsPar{} projects.
    A project may have support to more than one parallel mode. Also,
    a project may run only a subset tests in parallel by default.}
\end{figure}

@@

\subsubsection{Support of parallelization configuration in build files}

We complemented our previous investigation with a static analysis of
several \pomf{} files from the \numMedLong{} subjects. The rationale
is that some projects might not enable parallelism in the default
execution. \Jbc{Remember to explain that we need the previous analysis
because some configurations are unreachable statically when inherited
from some external module}.

%% To answer \numRQC{} we initially mined build files (\ie, \pomf{}) .
%% must contain one of these keywords that
%% contain parallelization keywords, namely \CodeIn{forkMode},
%% \CodeIn{forkCount}, and \CodeIn{parallel}.

This mining step, however, is not sound as a matching project may not
indicate a project with a valid configuration for running tests in
parallel.  False positive can happen because of comments, for
instance.  To eliminate the cases of false positives and also to
categorize true positive cases, we complemented the initial mining
step with a manual inspection of files.

@@

From the \numMedLong{} subjects, we found \pomMedLong{} \pomf{} files
where \numPomMatched{} of those files match one of the keywords
mentioned above.  From these \numPomMatched{} build files, we
eliminated six false-positives: two were names of project modules
(\eg, \emph{camel-cookbook-parallel-processing}), one was part of a
comment, and three were commented configurations. The
\numPomMatchedValid{} build files with valid configurations are
distributed across \numProjectsPar{} projects from our sample.
\emph{From these results we found that $\sim$51\% of medium and
long-running projects do not use parallel features to run test
suites.}\Mar{please make it consistent with research
question}\Mar{explain this is over(under)-estimated...}

@@

To answer \numRQD{}, we considered the \numProjectsPar{} subjects with
parallelization settings identified in \numRQC{} and compared their
time cost with sequential execution. We are interested in measuring the
execution speedup (if any) when the parallelization settings are
activated.
\Jbc{explain methodology}.

>>>>

\Jbc{these results will be updated $\rightarrow$} It is important to
mention that Figure~\ref{fig:rq1-barplot} represents a lower bound
estimation for time cost because some tests may finish earlier than
expected due to existing bugs on the ongoing revision.  From the
\numSubjs{} compiled projects, \numSubjsPass{} successfully executed
all tests and \numSubjsFail{} reported test failures.  Also, some
projects omit long-running tests on their default execution. For
instance, it is necessary to invoke Maven with additional parameters
to run integration tests from project \CodeIn{apache.maven-surefire}
(nearly 30 min in our environment).

@@

To evaluate the support of parallelization to run tests, we
investigate if there are projects with parallel execution enabled by
default and what configurations are more popular. In addition, we
complement our investigation by analyzing several build files (\ie,
\pomf{}) to identify projects that supports parallel execution but
require additional execution parameters to enable this feature.  We
describe our approach as follows:

\subsubsection{Test execution with parallelism enabled by default}
\label{sec:rqC-1}

Initially, we configured Maven to output all configuration variables.
The rationale is that, for each project's module, we can capture
relevant configurations and classify their parallelization level (see
Section \ref{sec:modes}) based on their values. To avoid waiting all
tests to terminate, we just run the bootstrap phase and we skip the
actual test execution.

According to Maven's documentation \Fix{cite surefire doc}, any
parallelization setting depends either on (1) \CodeIn{parallel} to
define the parallelism level within a JVM followed by
\CodeIn{threadCounter} or (2) \CodeIn{forkCount} (or \CodeIn{forkMode}
in older versions) to define the number of forked JVMs. For each test
execution, we look for theses parameters and their values to classify
them.  \Jbc{Missing: explain how we mapped the configurations to
parallel level.} Figure~\ref{fig:freqmodes-dynamic} summarizes our
findings.

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.32\textwidth]{plots/barplot-modes-dynamic.pdf}
    \caption{\label{fig:freqmodes-dynamic}\Fix{fix
    caption}Distribution of parallel modes identified dynamically in a
    subset of \numProjectsPar{} projects.  A project may have support
    to more than one parallel mode. Also, a project may run only a
    subset tests in parallel by default.}
\end{figure}

@@

\subsubsection{Support of parallelization configuration in build files}
\label{sec:rqC-2}

% considered all projects classified as \medg{} and \longg{}-running, a
% total of \numMedLong{} subjects (see Figure~\ref{fig:rq1-barplot}). To
% reduce noise we did not consider projects with \shortg{}-running test
% suites as we observed that \percentShortSequential{} of those projects
% do not use parallelism; including them would favor sequential
% execution in our analysis.

To extend our initial investigation, we mined several \pomf{} files
must contain one of these keywords that contain parallelization
keywords, namely \CodeIn{forkMode}, \CodeIn{forkCount}, and
\CodeIn{parallel}.  This mining step, however, is not sound as a
matching project may not indicate a project with a valid configuration
for running tests in parallel.  False positive can happen because of
comments, for instance.  To eliminate the cases of false positives and
also to categorize true positive cases, we complemented the initial
mining step with a manual inspection of files.

@@

From the \numMedLong{} subjects, we found \pomMedLong{} \pomf{} files
where \numPomMatched{} of those files match one of the keywords
mentioned above.  From these \numPomMatched{} build files, we
eliminated six false-positives: two were names of project modules
(\eg, \emph{camel-cookbook-parallel-processing}), one was part of a
comment, and three were commented configurations. The
\numPomMatchedValid{} build files with valid configurations are
distributed across \numProjectsPar{} projects from our sample.
% 
% \emph{From these results we found that $\sim$51\% of medium and
% long-running projects do not use parallel features to run test
% suites.}\Mar{please make it consistent with research
% question}\Mar{explain this is over(under)-estimated...}

@@

To answer \numRQD{}, we considered the \numProjectsPar{} subjects with
parallelization settings enabled by default identified in \numRQC{}
and compared their time cost with sequential execution. We are
interested in measuring the execution speedup (if any) when the
parallelization settings are activated. It is important to mention
that we ignored the remaining \Fix{??} subjects identified in
Section~\ref{sec:rqC-2} because it would be impractical to execute
each subject on specific conditions to measure the impact of
parallelization.

To enforce sequential execution, \Jbc{explain methodology}.
